Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-08-31 ms/manuscript.Rmd
Change names of some raw data files

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "aic_env_repro",
  "binary_sig_results",
  "biodiv_ferns_cent",
  "biodiv_ferns_spatial",
  "broad_alignment_list",
  "comm_ferns",
  "comm_ferns_full",
  "csl_file",
  "fern_traits",
  "green_list",
  "japan_fern_tree",
  "japan_points_raw",
  "japan_pterido_tree",
  "japan_rbcL",
  "japan_shp",
  "k_phylogeny",
  "k_taxonomy",
  "lat_span_summary",
  "lrt_results",
  "model_fits",
  "model_params",
  "ms_functions",
  "occ_point_data_summary",
  "phy_sig_results",
  "plastome_calibration_dates",
  "plastome_tree",
  "ppgi",
  "protected_areas",
  "refs_other_yaml",
  "refs_yaml",
  "repro_data",
  "signif_cells_protected_area",
  "template_file",
  "traits_summary"
))
```

@@

# Modify dataframe to include formatting for printing label on map
japan_points <- 
  japan_points_raw %>%
  filter(is.na(lat_end)) %>%
  select(-lat_end, -lon_end) %>%
  mutate(
    label = case_when(
      # Print main islands in bold
      query %in% main_islands ~ glue::glue("**{query}**"),
      TRUE ~ query
    ),
    nudge = case_when(
      query == "Honshu" ~ "-0.5,-.7",
      query == "Tokyo" ~ "-1.2,0",
      query == "Shikoku" ~ "1.3,-.6",
      query == "Kyushu" ~ "1.6,-.4",
      query == "Miyako" ~ "1.5, 0",
      query == "Iriomote" ~ "1.8, 0",
      query == "Izu Islands" ~ "2.0, 0",
      query == "Yakushima" ~ "2.2, 0",
      query == "Ogasawara Islands" ~ "3.0, 0",
      query == "Izu Peninsula" ~ "2.0, -0.3",
      query == "Kii Peninsula" ~ "2.0, -0.5",
      query == "Ryukyu Islands" ~ "8.0, 1.0",
      query %in% small_islands ~ "2.0, 0",
      TRUE ~ "0,0"
    )
  ) %>%
  separate(nudge, c("nudge_lon", "nudge_lat"), sep = ",") %>%
  mutate(across(c(nudge_lon, nudge_lat), as.numeric)) %>%
  mutate(
    lon_adj = lon + nudge_lon,
    lat_adj = lat + nudge_lat
  )

japan_lines <- japan_points_raw %>%
  filter(!is.na(lat_end))

>>>>

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "aic_env_repro",
  "binary_sig_results",
  "biodiv_ferns_cent",
  "biodiv_ferns_spatial",
  "broad_alignment_list",
  "comm_ferns",
  "comm_ferns_full",
  "csl_file",
  "fern_traits",
  "green_list",
  "japan_fern_tree",
  "japan_map_points",
  "japan_pterido_tree",
  "japan_rbcL",
  "japan_shp",
  "k_phylogeny",
  "k_taxonomy",
  "lat_span_summary",
  "lrt_results",
  "model_fits",
  "model_params",
  "ms_functions",
  "occ_point_data_summary",
  "phy_sig_results",
  "plastome_calibration_dates",
  "plastome_tree",
  "ppgi",
  "protected_areas",
  "refs_other_yaml",
  "refs_yaml",
  "repro_data",
  "signif_cells_protected_area",
  "template_file",
  "traits_summary"
))
```

@@

# Modify dataframe to include formatting for printing label on map
japan_points <- 
  japan_map_points %>%
  filter(is.na(lat_end)) %>%
  select(-lat_end, -lon_end) %>%
  mutate(
    label = case_when(
      # Print main islands in bold
      query %in% main_islands ~ glue::glue("**{query}**"),
      TRUE ~ query
    ),
    nudge = case_when(
      query == "Honshu" ~ "-0.5,-.7",
      query == "Tokyo" ~ "-1.2,0",
      query == "Shikoku" ~ "1.3,-.6",
      query == "Kyushu" ~ "1.6,-.4",
      query == "Miyako" ~ "1.5, 0",
      query == "Iriomote" ~ "1.8, 0",
      query == "Izu Islands" ~ "2.0, 0",
      query == "Yakushima" ~ "2.2, 0",
      query == "Ogasawara Islands" ~ "3.0, 0",
      query == "Izu Peninsula" ~ "2.0, -0.3",
      query == "Kii Peninsula" ~ "2.0, -0.5",
      query == "Ryukyu Islands" ~ "8.0, 1.0",
      query %in% small_islands ~ "2.0, 0",
      TRUE ~ "0,0"
    )
  ) %>%
  separate(nudge, c("nudge_lon", "nudge_lat"), sep = ",") %>%
  mutate(across(c(nudge_lon, nudge_lat), as.numeric)) %>%
  mutate(
    lon_adj = lon + nudge_lon,
    lat_adj = lat + nudge_lat
  )

japan_lines <- japan_map_points %>%
  filter(!is.na(lat_end))
